Helmet Foam Case Study Report

### 2024-05-07 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd

@@

```{r}
#| echo: false
#| label: fig-3
#| warning: false
#| fig-cap: "Log(stiffnessFrac) vs Log(cycle) and Log(dampingFrac) vs Log(cycle), Colored by Freq"
#| fig-align: "center"
#| fig-width: 10
#| fig-height: 5

sp1 <- ggplot(foam_data_scaled, aes(y = log(stiffnessFrac), x = log(cycle))) + geom_point(aes(color = freq))
#sp2 <- ggplot(foam_data_scaled, aes(y = log(stiffnessFrac), x = log(cycle))) + geom_point(aes(color = factor(chemIndex)))
#sp3 <- ggplot(foam_data_scaled, aes(y = log(stiffnessFrac), x = log(cycle))) + geom_point(aes(color = porosity))

#combined <- sp1 + sp2 + sp3

#combined

dp1 <- ggplot(foam_data_scaled, aes(y = log(dampingFrac), x = log(cycle))) + geom_point(aes(color = freq))
#dp2 <- ggplot(foam_data_scaled, aes(y = log(dampingFrac), x = log(cycle))) + geom_point(aes(color = factor(chemIndex)))
#dp3 <- ggplot(foam_data_scaled, aes(y = log(dampingFrac), x = log(cycle))) + geom_point(aes(color = porosity))

#combined <- dp1 + dp2 + dp3

#combined

@@

@@

From @Table-1, we see a high significance in our coefficients. Some variables are not significant on their own, their interactions with log(cycle) are. For example, chemical index does not appear to have a significant relationship with the response on it's own, but one level of chemical index has a significant relationship when interacted with log(cycle). The interaction terms explain how log(cycle) effects stiffness fraction differently under different conditions. From this summary, amplitude appears to have the largest positive impact on initial stiffness fraction, and the largest negative impact as time progresses.

```{r, echo = FALSE}
#| echo: false
#| label: Table-1
#| warning: false
#| fig-cap: "Coefficients for Stiffness Fraction Model"
#| fig-align: "center"
#| fig-width: 7
#| fig-height: 4
library(car)
suppressWarnings(FactorModel1 <- lmer(log(stiffnessFrac) ~ factor(chemIndex) + freq + amp +  log(cycle) +  factor(chemIndex):log(cycle) +  freq:log(cycle) + amp:log(cycle) + (1 + log(cycle)|ID), data = foam_data_scaled))
summary(FactorModel1)$coef
```

Although @Table-1 indicates there is significance to the different levels of chemical index, the output below in @Table-2 confirms that there is a significant difference between at least one of the levels of chemical index. To further assess the significance of the model, we used diagnostic plots to find that this model meets the linearity, normality, and equal variance conditions. These plots are in the appendix.

```{r, echo = FALSE}
#| echo: false
#| label: Table-2
#| warning: false
#| fig-cap: "Anova Analysis of Stiffness Fraction Model"
#| fig-align: "center"
#| fig-width: 7
#| fig-height: 4
Anova(FactorModel1)
```

>>>>

\newpage

@@

```{r}
#| echo: false
#| label: fig-3
#| warning: false
#| fig-cap: "Log(stiffnessFrac) vs Log(cycle) and Log(dampingFrac) vs Log(cycle), Colored by Freq"
#| fig-align: "center"
#| fig-width: 10
#| fig-height: 4

sp1 <- ggplot(foam_data_scaled, aes(y = log(stiffnessFrac), x = log(cycle))) + geom_point(aes(color = freq))

@@

\begin{center}
\text{Table 4: Selected Predictors}
\end{center}

@@

```{r, echo = FALSE}
library(car)
suppressWarnings(FactorModel1 <- lmer(log(stiffnessFrac) ~ factor(chemIndex) + freq + amp +  log(cycle) +  factor(chemIndex):log(cycle) +  freq:log(cycle) + amp:log(cycle) + (1 + log(cycle)|ID), data = foam_data_scaled))
summary(FactorModel1)$coef
```

\begin{center}
\text{Table 5: Coefficients for Stiffness Fraction Model}
\end{center}

In Table 5, we see high significance (aka p-value < 0.05) for most of our coefficients. Some variables are not significant on their own, their interactions with log(cycle) are. For example, chemical index does not appear to have a significant relationship with the response on it's own, but one level of chemical index has a significant relationship when interacted with log(cycle). The interaction terms explain how log(cycle) effects stiffness fraction differently under different conditions. From this summary, amplitude appears to have the largest positive impact on initial stiffness fraction, and the largest negative impact as time progresses.

Although Table 5 indicates chemical index levels 2 and 3 (aka 100 and 121) are not significant, the output below in Table 6 confirms that at least one chemical index is significantly different from another. To further assess the model, we used diagnostic plots to find that it meets the linearity, normality, and equal variance conditions. These plots are in the appendix.

```{r, echo = FALSE}
Anova(FactorModel1)
```

\begin{center}
\text{Table 6: Anova Analysis of Stiffness Fraction Model}
\end{center}
